Iterative Ground State Approach Algorithm

### 2024-11-24 TilingProjectDraft/tilingProject.tex
extended by keeping more states, and created final polished plots
corrected analytic tiling expressions for static correlations, enhanced iterdiag notes

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.23\textwidth]{SF-3.pdf}
	\includegraphics[width=0.23\textwidth]{SF-4.pdf}
	\includegraphics[width=0.23\textwidth]{SF-5.pdf}
	\includegraphics[width=0.23\textwidth]{SF-6.pdf}
	\caption{\(k-\)space distribution of spin-flip scattering correlation \(\chi_s(d,\vec k)\) (defined in the main text). The last three figures \((W/J=-1.74, -1.83, -1.84)\) show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last \(k-\)point to decouple from the impurity.}
	\label{spinCorr}
\end{figure}

@@

Studies of \(k-\)space mutual information, \(I_2(\vec k, k_\text{N})\) and \(I_2(\vec k, k_\text{AN})\), between any given \(k-\)state and the node and antinode respectively, have revealed that each point interacts most strongly with it's own neighbourhood (see Supplementary Materials). This feature is in contrast to the charge-transfer correlations in the bath, that show ``long-ranged" interactions between the node and the antinode. These correlations will be discussed immediately after this, and are primarily responsible for driving the impurity transition and destabilising the Kondo cloud.
\begin{figure}[!htpb]
	\centering
	\includegraphics[width=0.23\textwidth]{I2_k_d-1.pdf}
	\includegraphics[width=0.23\textwidth]{I2_k_d-2.pdf}
	\caption{\(k-\)space distribution of entanglement entropy. The pseudogapping occurs through (i) suppression of entanglement at \(W/J=-1.74\) near the nodes (compared to \(W=0\)), (ii) vanishing of entanglement near the antinodes, (iii) vanishing of entanglement at all points except the node.}
	\label{vneKspace}
\end{figure}

@@

\subsection{Momentum-space Greens functions}
We now consider Greens functions at a particular momentum \({\bf K}\), obtained by setting \(\nu_1=\nu_2={\bf K}\). The spectral coefficients are of the form
\begin{equation}\begin{aligned}
	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
	F_{c^\dagger}(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_d^\prime)}~.
\end{aligned}\end{equation}
Similar to the approach for the real-space Greens function, we simplify \(F^*_p(s, {\bf K})\) by retaining only the \({\bf r}_d = {\bf r}_d^\prime\) members, and then translating the arbitrary point \({\bf r}_d\) to a common reference point \({\bf r}_c\) in the lattice:
\begin{equation}\begin{aligned}
	&F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}~,\\
	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
	&= \braket{\psi_{n_0}({\bf r}_c)| T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}~.
\end{aligned}\end{equation}
The effect of the translation operators on the \(k-\)space annihilation operator can be easily deduced by transforming it to real-space, using the Fourier transform definition
\begin{equation}\begin{aligned}\label{fourTransf}
	c({\bf K}) = \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r})~.
\end{aligned}\end{equation}
Upon applying this, we get
\begin{equation}\begin{aligned}\label{translationOnField}
	&T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r} - {\bf r}_d + {\bf r}_c)\\
	&= e^{i{\bf K}\cdot\left({\bf r}_d - {\bf r}_c\right)}c({\bf K})~.
\end{aligned}\end{equation}
With this, the final form of \(F_{c^\dagger}^*(s, {\bf K})\) becomes
\begin{equation}\begin{aligned}
	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}e^{-i {\bf K}\cdot{\bf r}_c}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\\
	\times\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d}
\end{aligned}\end{equation}
The sum over \({\bf r}_d\) evaluates to \(\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} = N \delta_{{\bf K}, - {\bf k} + {\bf k}_0}\), leading to
\begin{equation}\begin{aligned}
	F_{c^\dagger}^*(s, {\bf K}) = e^{-i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, - {\bf k} + {\bf k}_0}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}
\end{aligned}\end{equation}

@@

One can also look at \(k-\)space correlations, of the spin or charge kind:
\begin{equation}\begin{aligned}
	\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) + \text{h.c.}}~,\\
	\tilde{C}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{C^+\left({\bf K}_1\right)C^-\left({\bf K}_2\right) + \text{h.c.}}~.
\end{aligned}\end{equation}
We again consider the spin-flip correlation first. In order to introduce the impurity site, we rewrite the expectation values as
\begin{equation}\begin{aligned}
	&\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) \\
	&= \frac{1}{2}\left[\sqrt{\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)}\braket{S^-\left({\bf K}_2\right)S^+\left({\bf K}_1\right)}} + \text{h.c.}\right] ~.
\end{aligned}\end{equation}
We frame this in terms of the auxiliary model by (i) making the substitution again for the ground states, and (ii) by fourier transforming the first operator within each expectation value to real space and retaining just the impurity site operator:
\begin{equation}\begin{aligned}
	&\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) \\
	&= \frac{1}{2}\left[\sqrt{\braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf d}\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}}\right. \\
	&\left.\times\sqrt{\braket{\psi_\text{gs}{({\bf r}_c)} | S^-\left({\bf d}\right)S^+\left({\bf K}_1\right) | \psi_\text{gs}{({\bf r}_c)}}} + \text{h.c.}\right] ~.
\end{aligned}\end{equation}
Performing similar manipulations with the charge isospin-flip correlation gives
\begin{equation}\begin{aligned}
	&\tilde{C}_\text{flip}({\bf K}_1, {\bf K}_2) \\
	&= \frac{1}{2}\left[\sqrt{\braket{\psi_\text{gs}({\bf r}_c) | C^+\left({\bf d}\right)C^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}}\right. \\
	&\left.\times\sqrt{\braket{\psi_\text{gs}{({\bf r}_c)} | C^-\left({\bf d}\right)C^+\left({\bf K}_1\right) | \psi_\text{gs}{({\bf r}_c)}}} + \text{h.c.}\right] ~.
\end{aligned}\end{equation}

>>>>

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.23\textwidth]{SF-1.pdf}
	\includegraphics[width=0.23\textwidth]{SF-3.pdf}
	\includegraphics[width=0.23\textwidth]{SF-5.pdf}
	\includegraphics[width=0.23\textwidth]{SF-6.pdf}
	\caption{\(k-\)space distribution of spin-flip scattering correlation \(\chi_s(d,\vec k)\) (defined in the main text). The last three figures \((W/J=-1.74, -1.83, -1.84)\) show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last \(k-\)point to decouple from the impurity.}
	\label{spinCorr}
\end{figure}

@@

Studies of \(k-\)space mutual information, \(I_2(\vec k, k_\text{N})\) and \(I_2(\vec k, k_\text{AN})\), between any given \(k-\)state and the node and antinode respectively, have revealed that each point interacts most strongly with it's own neighbourhood (see Supplementary Materials). This feature is in contrast to the charge-transfer correlations in the bath, that show ``long-ranged" interactions between the node and the antinode. These correlations will be discussed immediately after this, and are primarily responsible for driving the impurity transition and destabilising the Kondo cloud.

@@

\subsection{Momentum-space Greens functions}
We now consider Greens functions at a particular momentum \({\bf K}\), obtained by setting \(\nu_1=\nu_2={\bf K}\). The spectral coefficients are of the form
\begin{equation}\begin{aligned}
	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
	F_{c^\dagger}(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_d^\prime)}~.
\end{aligned}\end{equation}
Similar to the approach for the real-space Greens function, we simplify \(F^*_p(s, {\bf K})\) by retaining only the \({\bf r}_d = {\bf r}_d^\prime\) members, and then translating the arbitrary point \({\bf r}_d\) to a common reference point \({\bf r}_c\) in the lattice:
\begin{equation}\begin{aligned}
	&F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}~,\\
	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
	&= \braket{\psi_{n_0}({\bf r}_c)| T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}~.
\end{aligned}\end{equation}
The effect of the translation operators on the \(k-\)space annihilation operator can be easily deduced by transforming it to real-space, using the Fourier transform definition
\begin{equation}\begin{aligned}\label{fourTransf}
	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r})~.
\end{aligned}\end{equation}
Upon applying this, we get
\begin{equation}\begin{aligned}\label{translationOnField}
	&T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r} - {\bf r}_d + {\bf r}_c)\\
	&= e^{i{\bf K}\cdot\left({\bf r}_d - {\bf r}_c\right)}c({\bf K})~.
\end{aligned}\end{equation}
With this, the final form of \(F_{c^\dagger}^*(s, {\bf K})\) becomes
\begin{equation}\begin{aligned}
	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}e^{-i {\bf K}\cdot{\bf r}_c}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\\
	\times\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d}
\end{aligned}\end{equation}
The sum over \({\bf r}_d\) evaluates to \(\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} = N \delta_{{\bf K}, - {\bf k} + {\bf k}_0}\), leading to
\begin{equation}\begin{aligned}
	F_{c^\dagger}^*(s, {\bf K}) = e^{-i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, - {\bf k} + {\bf k}_0}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}
\end{aligned}\end{equation}

@@

One can also look at \(k-\)space correlations, of the spin or charge kind:
	\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) + \text{h.c.}}~,\\
	\tilde{C}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{C^+\left({\bf K}_1\right)C^-\left({\bf K}_2\right) + \text{h.c.}}~.
We again consider the spin-flip correlation first. In order to introduce the impurity site, we rewrite the expectation values sum of all coherent scattering processes involving the impurity site and the two \(k-\)states. Using eq.~\ref{eigenstateProposal}, we express the correlation in terms of a single auxiliary model:
	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} \\
	&= \frac{1}{N}\sum_{{\bf r}_d}\braket{\psi_\text{gs}({\bf r}_d) | S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_d)}~,
where \({\bf r}_d\) is the location of the impurity site, and we average over the correlation values calculated over all possible auxiliary models. Assuming translation invariance, the static correlation values should be equal on every auxiliary model, allowing us to replace the average with the value at the reference origin \({\bf r}_c\):
\begin{equation}\begin{aligned}\label{correlationAuxiliary}
	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} = \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}~.
Using the definition \(S^+(\nu) = c^\dagger_{\nu \uparrow} c_{nu \downarrow}\), one can Fourier transform the fermionic operators in eq.~\ref{correlationAuxiliary},
	c_{{\bf k}\sigma} = \sum_{\bf r} e^{i {\bf k}\cdot{\bf r}} c_{{\bf r}\sigma},
and retain the only impurity site contribution \({\bf r}={\bf r}_c\) in order to introduce the dynamics of the impurity site. Carrying this out for one and two fermionic operators gives
\begin{equation}\begin{aligned}\label{correlationAuxiliaryProcess}
	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} \\
	&= \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}\\
	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}\\
	&+ \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right) c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
	&+ \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right) c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}~.
We haven't considered three-particle dynamics on the impurity site because those would involve only one momentum state and would hence be incoherent for the other momentum state; for the same reason, certain two-particle terms have also been ignored. Henceforth, we replace the index \({\bf r}_c\) with \(d\), indicating that it is the position of the impurity site. By introducing the off-site spin operator \(S^+_{\nu_1,\nu_2} = c^\dagger_{\nu_1 \uparrow} c_{\nu_2 \downarrow}\) that flips an effective spin across multiple orbitals, we can express eq.~\ref{correlationAuxiliaryProcess} in a more illuminating form:
	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} =\\
	& \braket{(S^+_{d, {\bf K}_1} + S^+_{{\bf K}_1,d}) S^-({\bf K}_2) + S^+({\bf K}_1) (S^-_{d, {\bf K}_2} + S^-_{{\bf K}_2, d}) \right.\\
	&+ \left.S^+_{d, {\bf K}_1} (S^-_{{\bf K}_2, d} + S^-_{d, {\bf K}_2}) + (S^+_{{\bf K}_1, d} + S^+_{{\bf K}_1, d}) S^-_{{\bf K}_2, d}}~.
This allows us to visualise the \(k-\)space correlation function through various scattering processes within the auxiliary model: the net correlation between \({\bf K}_1\) and \({\bf K}_2\) occur either through (i) simultaneous and opposite flips of the spin on one momentum state and the shared spin on the impurity site and another momentum state, or (ii) the simultaneous flips of spins shared between all three members.

The charge correlations can be treated exactly the same way. We quote the final result here, in terms of the off-site charge operators \(C^+_{\nu_1, \nu_2} = c^\dagger_{\nu_1 \uparrow} c^\dagger_{\nu_2 \downarrow}\) :
\begin{equation}\begin{aligned}
	&\left<C^+({\bf K}_1) C^-({\bf K}_2)\right> = \\
	& \braket{(C^+_{d, {\bf K}_1} + C^+_{{\bf K}_1,d}) C^-({\bf K}_2) + C^+({\bf K}_1) (C^-_{d, {\bf K}_2} + C^-_{{\bf K}_2, d}) \right.\\
	&+ \left.C^+_{d, {\bf K}_1} (C^-_{{\bf K}_2, d} + C^-_{d, {\bf K}_2}) + (C^+_{{\bf K}_1, d} + C^+_{{\bf K}_1, d}) C^-_{{\bf K}_2, d}}~.
\end{aligned}\end{equation}

### 2024-11-24 iterDiagAlgorithm/iterDiagAlgo.tex
corrected analytic tiling expressions for static correlations, enhanced iterdiag notes

\title{Iterative Ground State Approach Algorithm}
\begin{abstract}
	The following is the algorithm for performing an iterative diagonalization of fermionic systems. It is mostly similar to DMRG and NRG, and allows obtaining the low-energy spectrum large many-body Hamiltonians.
\end{abstract}
\date{\today}
\maketitle

%

@@

\section{Examples and Benchmarks}
\subsection{Single-Impurity Anderson Model}
The single-impurity Anderson model at half-filling is obtained by setting \(H_\text{imp}=-\frac{U}{2}\left(n_{d \uparrow} - n_{d \downarrow}\right)^2 \) and \(H_\text{imp-bath} = -V\sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)\) in eq.~\ref{hamiltonian}. We studied this model using the above approach to benchmark the ground state energy and spin-flip correlation \(\left<\frac{1}{2}S_d^+ S_0^- + \text{h.c.} \right>\) against exact diagonalization (ED). In order to extend the ED to a larger number of sites, we restricted ourselves to just the \(N=2\) sector, \(N\) being the total occupancy. We find very good agreement for \(M_s \sim 1000\) and above. These results are shown in Fig.~\ref{comparisonSIAM}.
\begin{figure*}[!htpb]
\centering
\includegraphics[width=0.48\textwidth]{energy.pdf}
\includegraphics[width=0.48\textwidth]{spinflipcomparison.pdf}
\label{comparisonSIAM}
\end{figure*}
\end{document}

>>>>

\title{Iterative Ground State Approach Algorithm}
\begin{abstract}
	The following is the algorithm for performing an iterative diagonalization of fermionic systems. It is mostly similar to DMRG and NRG, and allows obtaining the low-energy spectrum of large many-body Hamiltonians.
\end{abstract}
\date{\today}
\maketitle

\section{Introduction}
The broad idea is the following. We have a Hamiltonian describing an interacting set of states (in real or momentum space). We can express the total Hamiltonian in an incremental fashion: \(H = \sum_i H_i\), where \(H_{i+1}\) involves more number of states than \(H_i\). For example, a tight-binding model can be written in that form, with the definition \(H_i = c^\dagger_{i+1}c_i + \text{h.c.}\). The iterative diagonalisation method obtains the low-energy spectrum of this problem in the following manner: We first diagonalise the Hamiltonian \(H\) for a smaller value of \(i\), small enough such that this can be done exactly. We then truncate the spectrum to a predefined size, and rotate all existing operators to this truncated basis, including the Hamiltonian \(H\). We then consider the "bonding Hamiltonian" \(\Delta H\) between the existing sites and the new sites, and rotate the same into the truncated basis. Adding the previous rotated Hamiltonian \(H\) and the rotated increment Hamiltonian \(\Delta H\) gives us a truncated but effective Hamiltonian for the increased number of sites. We again diagonalise this, and again retain only a fixed number of states in the spectrum. We keep repeating this until we reach the required number of sites.

@@

\section{Examples and Benchmarks}
\subsection{Single-Impurity Anderson Model}
The single-impurity Anderson model at half-filling is obtained by setting \(H_\text{imp}=-\frac{U}{2}\left(n_{d \uparrow} - n_{d \downarrow}\right)^2 \) and \(H_\text{imp-bath} = -V\sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)\) in eq.~\ref{hamiltonian}. We studied this model using the above approach to benchmark the ground state energy and spin-flip correlation \(\left<\frac{1}{2}S_d^+ S_0^- + \text{h.c.} \right>\) against exact diagonalization (ED). In order to extend the ED to a larger number of sites, we restricted ourselves to just the \(N=2\) sector, \(N\) being the total occupancy. We find very good agreement for \(M_s \sim 1000\) and above. These results are shown in Fig.~\ref{comparisonSIAM}.
\begin{widetext}
\includegraphics[width=0.48\textwidth]{energy.pdf}
\includegraphics[width=0.48\textwidth]{spinflipcomparison.pdf}
\label{comparisonSIAM}
\end{widetext}
\end{document}
